---
title: "ProblemSet2Skills"
author: "Vera Jónsdóttir"
date: "4/12/2021"
output: html_document
---

```{r}
install.packages("dslabs")
install.packages("ggplot2")
library(ggplot2)
```


1 Git Concepts
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# git is a software for distributed version control. List 4 benefits of 
# distributed version control.
?git
```
2.1  Debugging mindset
2.1.1
```{r}
my_variable <- 10
my_varıable
```
This code runs smoothly in my laptop. However, there may be an issue with 
running the second variable as it is not written in the same way as the first
line of code.

2.1.2 Fix the following code so it works
```{r}

View(polls_us_election_2016)
library(dslabs)
ggplot(data = polls_us_election_2016) +
  geom_point(mapping = aes(x = startdate,
                           y = rawpoll_trump))

filter(data = polls_us_election_2016, state = Florida)
filter(diamonds, carat > 3)
?diamonds

```
2.1.3.Press Alt (Option) + Shift + K. What happens? How can you get to the same place using the menus?
```{r}
#Alt (Option) + Shift + K shows us a preview of Keyboard Shortcut Quick References
```

2.2  Filter 
2.2.1. Using thepolls_us_election_2016data frame in thedslabspackage find the following
2.2.1.1. Polls for the states of Hawaii and Alaska
```{r}
ggplot(data = polls_us_election_2016, mapping = aes(x = year, y = gdp_c))+
geom_line()
```




