---
title: "ProblemSet2Skills"
author: "Vera Jónsdóttir"
date: "4/12/2021"
output: html_document
---

```{r}
install.packages("dslabs")
install.packages("ggplot2")
library(ggplot2)
library(dslabs)
library(tidyverse)
library(dplyr)
```


1 Git Concepts
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

git is a software for distributed version control. List 4 benefits of distributed version control
-good way to cooperate with others especially when many are working on code or projects
-good way to be able to reinstate old versions
-good way to back up work
-good way to keep track of big projects and to make sure everybody is using the same version
-use branches to safely experiment with projects with out destroying the original project


2.1  Debugging mindset
2.1.1
```{r}
my_variable <- 10
my_varıable
```
This code runs smoothly in my laptop. However, there may be an issue with 
running the second variable as it is not written in the same way as the first
line of code.

2.1.2 Fix the following code so it works
```{r}

View(polls_us_election_2016)
library(dslabs)
ggplot(data = polls_us_election_2016) +
  geom_point(mapping = aes(x = startdate,
                           y = rawpoll_trump))

filter(polls_us_election_2016, state == "Florida")
filter(polls_us_election_2016, as.numeric(grade) > 3)

```
2.1.3.Press Alt (Option) + Shift + K. What happens? How can you get to the same place using the menus?
```{r}
#Alt (Option) + Shift + K shows us a preview of Keyboard Shortcut Quick References. In order to do this from menus you need to go to tools-->keyboard shortcuts. 
```

2.2  Filter 
2.2.1. Using the polls_us_election_2016data frame in the ds labs package find the following
2.2.1.1. Polls for the states of Hawaii and Alaska
```{r}
filter(polls_us_election_2016, state == "Alaska" | state == "Hawaii")
```
2.2.1.2
```{r}
filter(polls_us_election_2016, samplesize > 500)
```
2.2.1.3
```{r}
pd <- c("YouGov", "Google Consumer Surveys", "SurveyMonkey")
filter(polls_us_election_2016, pollster %in% pd)

```
2.2.1.4
```{r}
filter(polls_us_election_2016, as.numeric(grade) == 10 & rawpoll_trump<30)
```
2.2.1.5
```{r}
filter(polls_us_election_2016, adjpoll_clinton >=40 & adjpoll_clinton <=60 )
```
2.2.1.6
```{r}
filter(polls_us_election_2016, rawpoll_trump >= rawpoll_clinton + 10)
```
2.2.1.7
```{r}
filter(polls_us_election_2016, rawpoll_mcmullin > 5)
```

2.2.2.1
```{r}
filter(polls_us_election_2016, rawpoll_trump > 60 & startdate>="2016-01-01" & startdate<="2016-01-31")
```
This is the poll.

2.2.2.1
```{r}
filter(polls_us_election_2016, is.na(grade))
```
you need to change it to is.na. Otherwise R Studio won't understand your function

2.2.2.2
```{r}
filter(polls_us_election_2016, is.na(rawpoll_mcmullin))

```
4,178 rows withh McMullin are n/a. McMullin may not be very popular in the race so they do not keep very accurate polls on his statistics. He is therefore missing from very many polls.

2.2.2.3
```{r}
filter(polls_us_election_2016, as.numeric(grade) == 9)
```
There is no n/a that comes up when we search specifically for a particular letter grade.
#*Think about what hint is supposed to mean*#

2.2.2.4
```{r}
filter(polls_us_election_2016,  is.na(grade) | as.numeric(grade)>0)
```
It leads to printing of all columns with every possible grade and n/a as well.

2.2.2.5
```{r}
filter(polls_us_election_2016,  is.na(grade) | as.numeric(grade) == 0)

```
Here we will only get the N/A columns.

2.3.1
```{r}
select(polls_us_election_2016, grade, grade, grade)
```
Nothing changes if you repeat the sane variable multiple times

2.3.2
```{r}
select(polls_us_election_2016, contains("RAW",ignore.case = TRUE))
```
2.3.3
```{r}
select(polls_us_election_2016, contains("clinton") | contains("trump"))
select(polls_us_election_2016,rawpoll_clinton:rawpoll_trump | adjpoll_clinton:adjpoll_trump )
select(polls_us_election_2016,rawpoll_clinton:adjpoll_trump &-rawpoll_johnson & -rawpoll_mcmullin)
```

3.1
```{r}
polls_us_election_2016 %>% arrange(desc(rawpoll_clinton))%>%head(1)
```
3.2
```{r}
polls_us_election_2016 %>% arrange(desc(samplesize))%>%head(5)
```
3.3
```{r}
polls_us_election_2016 %>% arrange(desc(is.na(rawpoll_johnson)))
polls_us_election_2016 %>% arrange(desc(is.na(rawpoll_clinton)))

```
4.1
```{r}
rawcandidate <- polls_us_election_2016 %>% 
  mutate(raw_trump=rawpoll_trump/100*samplesize) %>%       
  mutate(raw_clinton=rawpoll_clinton/100*samplesize) %>%
   mutate(raw_johnson=rawpoll_johnson/100*samplesize) %>%       
  mutate(raw_mcmullin=rawpoll_mcmullin/100*samplesize)

rawcandidate
```
4.2
```{r}
df1 <- rawcandidate %>% 
  mutate(new_variable=samplesize-(raw_trump+raw_clinton))
ggplot(data = df1,
       mapping = aes(x = startdate,
                     y = new_variable)) +
  geom_point() +
  geom_smooth(se=TRUE)
```
4.3
```{r}
df2 <- df %>% 
  mutate(new_variable=samplesize-(raw_trump+raw_clinton+raw_johnson+raw_mcmullin))
ggplot(data = df2,
       mapping = aes(x = startdate,
                     y = new_variable)) +
  geom_point() +
  geom_smooth(se=TRUE)
```
4.4
The reason why is because Johnson is such a big candidate and he polled very well close to the election. We also need to take McMuller out of the picture although he was less significant. He polled very well in Utah for example with 21.5 percent of the votes and third in Idaho.

4.5
Ths mostly fixes the problem since Johnson was such a big candidate and when he is out of the picture, there is very little disturbing the data.

4.6
```{r}
polls_us_election_2016 %>%
 select(startdate, pollster, rawpoll_johnson) %>%
 group_by(startdate) %>%
 mutate(rank = min_rank(desc(rawpoll_johnson)),ties.method = 'first')%>%
  head(20)

```
We break ties with the first row that comes up.

5.1
```{r}
polls_us_election_2016 %>%
count(pollster)

polls_us_election_2016 %>%
  group_by(pollster) %>%
  summarise(pollster_n=n())

```

5.2
```{r}
polls_us_election_2016 %>% 
  group_by(grade)%>%
  filter(state=="Florida")%>%
  summarise(mean=mean(samplesize))
```

5.3
```{r}
polls_us_election_2016 %>% 
  group_by(pollster)%>%
  count(grade)
```
It seems so?

5.4
```{r}
polls_us_election_2016 %>% 
  group_by(state)%>%
  arrange(rawpoll_mcmullin)
```
5.5
```{r}
polls_us_election_2016 %>%
  group_by(state) %>%
	summarize(pollster_n=n()) %>%
	filter(pollster_n>10) %>%
  arrange(desc(pollster_n))
```
5.65
```{r}
  polls_us_election_2016 %>%
	group_by(grade,population) %>%
	summarize(max_n=max(rawpoll_trump),min_n=min(rawpoll_trump)) %>%
  arrange(desc(max_n), desc(min_n))

```

5.7
```{r}
polls_us_election_2016 %>%
  group_by(state) %>%
	summarize(pollster_n=n()) %>%
  filter(state =="Alabama" | state == "Arkansas") %>%
  arrange(desc(pollster_n))
```
```{r}
polls_us_election_2016 %>%
  group_by(state) %>%
  filter(state !="Alabama" & state != "Arkansas") %>%
  summarize(pollster_n=n()) %>%
  arrange(desc(pollster_n))

```

They are running a total of 1106 polls in the United States excluding the polls in Alabama and Arkansas

6.1.a
```{r}
df3 <- polls_us_election_2016%>%
  mutate(spread=(rawpoll_trump - rawpoll_clinton)/100)
View(df3)

df4 <- polls_us_election_2016%>%
  mutate(spread=(rawpoll_trump - rawpoll_clinton)/100) %>%
  group_by(pollster) %>%
	summarize(spread, mean_spread_n=mean(spread))
df4


```

6.1.b.a
```{r}
df5 <- df3%>%
  mutate(p=(spread+1)/2)
  
View(df5)

```


6.1.b.b
```{r}

df6 <- df5%>%
  mutate(sd=2*sqrt((p*(1-p)/samplesize)))
View(df6)
  
```
It's true because this is a typical proportional sample and the two candidates dominate.

6.1.b.c
```{r}
df7 <-df6%>%
  mutate(lci=spread-qnorm(0.975)*sd) %>%
  mutate(uci=spread+qnorm(0.975)*sd) 
View(df7)
```
6.1.c
```{r}
df8<- df7%>%
  mutate(error=spread-0.021)
View(df8)

ggplot(data = df8, aes(x = startdate, y = error, 
                       group = pollster))+
  geom_point()
```
```{r}


ggplot(data = df8, aes(x = pollster, y = error, 
                       group = pollster))+
  geom_point()
```
```{r, fig.width=10,fig.height=25}
ggplot(data = df8, aes(x = error, y = pollster, 
                       group = pollster))+
  theme(axis.text.x = element_text(angle = 90))+
  geom_point()
```

```{r, fig.width=10,fig.height=25}
ggplot(data = df8, aes(x = error, y = pollster, 
                       group = pollster))+
  theme(axis.text.x = element_text(angle = 90))+
  geom_point()
```




2.2.2.1
```{r}
filter(polls_us_election_2016, rawpoll_trump > 60 & startdate>="2016-01-01" & startdate<="2016-01-31")
```
```{r}
filter(polls_us_election_2016, is.na(grade))
```
2.2.2.2
```{r}

```



