---
title: "ProblemSet2Skills"
author: "Vera Jónsdóttir"
date: "4/12/2021"
output: html_document
---

```{r}
install.packages("dslabs")
install.packages("ggplot2")
library(ggplot2)
library(dslabs)
library(tidyverse)
library(dplyr)
```


1 Git Concepts
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# git is a software for distributed version control. List 4 benefits of 
# distributed version control.
?git
```
2.1  Debugging mindset
2.1.1
```{r}
my_variable <- 10
my_varıable
```
This code runs smoothly in my laptop. However, there may be an issue with 
running the second variable as it is not written in the same way as the first
line of code.

2.1.2 Fix the following code so it works
```{r}

View(polls_us_election_2016)
library(dslabs)
ggplot(data = polls_us_election_2016) +
  geom_point(mapping = aes(x = startdate,
                           y = rawpoll_trump))

filter(polls_us_election_2016, state == "Florida")
filter(polls_us_election_2016, as.numeric(grade) > 3)

```
2.1.3.Press Alt (Option) + Shift + K. What happens? How can you get to the same place using the menus?
```{r}
#Alt (Option) + Shift + K shows us a preview of Keyboard Shortcut Quick References
```

2.2  Filter 
2.2.1. Using the polls_us_election_2016data frame in the ds labs package find the following
2.2.1.1. Polls for the states of Hawaii and Alaska
```{r}
filter(polls_us_election_2016, state == "Alaska" | state == "Hawaii")
```
2.2.1.2
```{r}
filter(polls_us_election_2016, samplesize > 500)
```
2.2.1.3
```{r}
filter(polls_us_election_2016, as.numeric(pollster) == 194 | 63 | 160)

```
2.2.1.4
```{r}
filter(polls_us_election_2016, as.numeric(grade) == 10 & rawpoll_trump<30)
```
2.2.1.5
```{r}
filter(polls_us_election_2016, adjpoll_clinton >=40 & adjpoll_clinton <=60 )
```
2.2.1.6
```{r}
filter(polls_us_election_2016, rawpoll_trump >= rawpoll_clinton + 10)
```
2.2.1.7
```{r}
filter(polls_us_election_2016, rawpoll_mcmullin =5)
```

2.2.2.1
```{r}
filter(polls_us_election_2016, rawpoll_trump > 60 & startdate>="2016-01-01" & startdate<="2016-01-31")
```
2.2.2.1
```{r}
filter(polls_us_election_2016, is.na(grade))
```
2.2.2.2
```{r}
filter(polls_us_election_2016, is.na(rawpoll_mcmullin))

```
4,178 rows withh McMullin are n/a. McMullin may not be very popular in the race so they do not keep very accurate polls on his statistics. 

2.2.2.3
```{r}
filter(polls_us_election_2016, as.numeric(grade) == 10)
```
There is no n/a that comes up when we search specifically for a particular letter grade.
#*Think about what hint is supposed to mean*#

2.2.2.4
```{r}
filter(polls_us_election_2016,  is.na(grade) | as.numeric(grade)>0)
```
It leads to printing of all columns with every possible grade and n/a as well.

2.2.2.5
```{r}
filter(polls_us_election_2016,  is.na(grade) | as.numeric(grade) == 0)

```
Here we will only get the N/A columns.

2.3.1
```{r}
select(polls_us_election_2016, grade, grade, grade)
```
Nothing changes if you repeat the sane variable multiple times

2.3.2
```{r}
select(polls_us_election_2016, contains("RAW",ignore.case = TRUE))
```
2.3.3
```{r}
select(polls_us_election_2016, contains("clinton") | contains("trump"))
select(polls_us_election_2016,rawpoll_clinton:rawpoll_trump | adjpoll_clinton:adjpoll_trump )
select(polls_us_election_2016,rawpoll_clinton:adjpoll_trump &-rawpoll_johnson & -rawpoll_mcmullin)
```

3.1
```{r}
polls_us_election_2016 %>% arrange(desc(rawpoll_clinton))%>%head(1)
```
3.2
```{r}
polls_us_election_2016 %>% arrange(desc(samplesize))%>%head(5)
```
3.3
```{r}
polls_us_election_2016 %>% arrange(desc(is.na(rawpoll_johnson)))
polls_us_election_2016 %>% arrange(desc(is.na(rawpoll_clinton)))

```
4.1
```{r}
df <- polls_us_election_2016 %>% 
  mutate(raw_trump=rawpoll_trump/100*samplesize) %>%       
  mutate(raw_clinton=rawpoll_clinton/100*samplesize) %>%
   mutate(raw_johnson=rawpoll_johnson/100*samplesize) %>%       
  mutate(raw_mcmullin=rawpoll_mcmullin/100*samplesize)

df
```
4.2
```{r}

```





2.2.2.1
```{r}
filter(polls_us_election_2016, rawpoll_trump > 60 & startdate>="2016-01-01" & startdate<="2016-01-31")
```
```{r}
filter(polls_us_election_2016, is.na(grade))
```
2.2.2.2
```{r}

```



